---
title: "Tidyverse Create"
author: "Coco Donovan"
date: "`r Sys.Date()`"
output: html_document
---

## Introduction:
Text

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading/Installing Packages

```{r}
library(ggplot2)
library(dplyr)
#tidyr
library(readr)
#purrr
#tibble
library(stringr)
#forcats
```

## readr

I used the read_csv() function to read in my csv of NCAA Women's Basketball 
roster info. Within read_csv() I used the col_types argument to change data types
of certain columns. Initially the columns that I changed inside read_csv() were
chr type, but to do meaningful analysis I needed to make them numerical, hence 
setting them to col_double() (which sets the data type of the column to a double).
This same logic can be applied to 
```{r}
ncaa_wbb_rosters <- read_csv('https://raw.githubusercontent.com/Sports-Roster-Data/womens-college-basketball/main/wbb_rosters_2022_23.csv', col_types = list(total_inches = col_double(), height_ft = col_double(), height_in = col_double()))

colnames(ncaa_wbb_rosters)

mean(ncaa_wbb_rosters$total_inches, na.rm = TRUE)

ncaa_wbb_rosters$total_inches <- col_double(ncaa_wbb_rosters$total_inches)
```



```{r}

```

## dyplr

### distinct()

I am unsure what values the redshirt column could possibly take on, so I use a 
pipe and the distinct() function to highlight the possible values 'redshirt' may 
take on. I find that redshirt can either be 1, for "yes, a student athlete was 
redshirted," or 0, for "no, a student athlete was not redshirted."

```{r}
ncaa_wbb_rosters %>%
  distinct(redshirt)
```



```{r}
summary_table <- ncaa_wbb_rosters %>%
  select('team', 'player_id', 'total_inches', 'country_clean', 'state_clean') %>%
  group_by(team) %>%
  summarize()

```
